%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1



%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-12pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]\vspace{3pt}}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{xcolor}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape  Bosco Chanam} \\ \vspace{0pt}
    \small +91 876-688-0662 $|$ \href{boscochanam@gmail.com}{\underline{boscochanam@gmail.com}}  $|$ 
    \href{https://www.linkedin.com/in/boscochanam/}{\underline{LinkedIn}} $|$
    \href{https://github.com/boscochanam}{\underline{Github}} \vspace{5pt} $|$ 
    \href{https://www.kaggle.com/boscochanam}{\underline{Kaggle}}
\end{center}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI ML SDE Engineer}{Aug 2024 -- Present}
      {Kalyani Group · Internship}{Pune, Maharashtra, India · On-site}
      \resumeItemListStart
        \resumeItem{Spearheading AI/ML initiatives at Bharat Forge, the World's Largest Forging Company, within a newly established AI/ML Incubation Centre.}
        \resumeItem{Focused on Computer Vision applications, developing and deploying cutting-edge models using TensorFlow, PyTorch, and OpenCV.}
        \resumeItem{Implementing end-to-end solutions, including model deployment via FastAPI and containerization with Docker, ensuring scalable and reliable performance.}
        \resumeItem{Exploring and integrating Large Language Models (LLMs) to enhance existing systems and drive innovation in AI/ML capabilities.}
        \resumeItem{Utilizing cloud services such as AWS for model training, deployment, and management.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Intern}{July 2023 -- Present}
      {Symbiosis Centre for Applied Artificial Intelligence}{Pune}
      \resumeItemListStart
        \resumeItem{Engaged in advanced research in multi-task learning methodologies, specifically tailored for computer vision applications.}
        \resumeItem{Developing state-of-the-art Computer Vision models for object detection in hand-drawn images, contributing to flagship projects.}
        \resumeItem{Experimenting with various deep learning architectures and optimization techniques to improve model accuracy and efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {Technical Co-Head}{July 2023 -- Present}
      {CodeX SIT}{Pune}
      \resumeItemListStart
        \resumeItem{Directed and conducted technical seminars and hands-on workshops, educating junior members in key technologies such as Python, Machine Learning, and Full Stack Development.}
        \resumeItem{Led technical initiatives and managed projects within the college club, fostering innovation and skill development.}
        \resumeItem{Mentored and trained club members in Full Stack Development, Data Science, and AI/ML, enhancing their technical proficiency and project execution capabilities.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Symbiosis Institute of Technology}{Pune}
      {Bachelor of Technology in Computer Science Engineering: 8 CGPA}{2021 - 2025}
    \resumeSubheading
      {The Orchid School}{Pune}
      {CBSE XII: 87.2\% }{2019 -- 2021}
    \resumeSubheading
      {Global Indian International School}{Pune}
      {CBSE X: 93.2\% }{2016 -- 2019}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\href{https://github.com/boscochanam/gesture-interfacing}{\textbf{Hand Gesture Recognition and Computer Interfacing}} $|$ \emph{Python, OpenCV, TensorFlow, CNN}}{2024}
\resumeItemListStart
\resumeItem{Developed a hand gesture recognition system to interpret and interact with computer interfaces.}
\resumeItem{Implemented computer vision techniques using OpenCV to capture and process hand gestures in real-time.}
\resumeItem{Implemented volume control, based on pinching distance, scroll up, scroll down, hand tracking for cursor}
\resumeItemListEnd

\resumeProjectHeading
    {\textbf{\href{https://github.com/boscochanam/circuit-component-detection}{Circuit Component Detection}} $|$ \emph{YOLO, Tensorflow}}{2024}
    \resumeItemListStart
        \resumeItem{
Integrated detection models into existing circuit analysis software for real-time component identification
 }
        \resumeItem{Successfully identified components along with spacial coordinates}
        \resumeItem{Shipped data to frontend via fastAPI for interactive experience}
    \resumeItemListEnd
\resumeProjectHeading
    {\href{https://github.com/boscochanam/facial-attribute-prediction}{\textbf{Facial Attribute Prediction}} $|$ \emph{Python, CNN, VGG, ResNet, Transfer Learning}}{2023}
    \resumeItemListStart
        \resumeItem{Developed a CNN Classifier for age, gender, and ethnicity prediction from facial images.}
        \resumeItem{Achieved high accuracy using deep learning techniques, including VGG and ResNet architectures.}
        \resumeItem{Leveraged Transfer Learning to improve prediction performance.}
    \resumeItemListEnd




\resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, HTML/CSS, MongoDB, SQL, TypeScript} \\
     \textbf{Frameworks}{: ReactJS, Flask, Bootstrap, Express, Node} \\
     \textbf{Libraries}{: Beautiful Soup, Hugging Face Transformers, VGG, ResNet, pandas, NumPy, Matplotlib, Seaborn} \\
     \textbf{Other Technologies}{: AWS, MySQL, MongoDB, Git, Prisma}
    }}
\end{itemize}

\section{Courses and Certifications}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-4 pt]
    \item Andrew Ng: Machine Learning Specialisation
    \item Jose Portilla: Python for Data Science and Machine Learning Bootcamp
    \item Jose Portilla: Probability and Statistics for Business and Data Science
    \item Angela Yu: 100 Days of Code, Python
\end{itemize}




%-------------------------------------------
\end{document}
